---
title: "Berlin_crimes_2012-2019"
author: "Garro"
date: "2023-08-10"
output: html_document
---


### Crimes in Berlin 2012-2019

For this exercise we will be using the dataset of crimes committed in Berlin for the period of 2012-2019, available in Kaggle https://www.kaggle.com/datasets/danilzyryanov/crime-in-berlin-2012-2019. 

*Note*: ctrl + alt + i (for a new chunk of code)

This dataset includes 16 categories of crimes and information pertaining the year and location where they occurred.

### Exercise 1 - Reading data and needed packages 

a) Read the dataset and load tidyverse. Is this tidydata? Use head(data) to find out.
```{r}
#YOUR CODE HERE
```

b) Let's transform the data to a friendlier format with pivot_wider()
```{r}
#YOUR CODE HERE
```

c) How many columns and rows are in the dataset? What are their types? Use the glimpse() function.

```{r}
#YOUR CODE HERE
```

### Exercise 2 - Let's explore the data

a) How many districts does Berlin have? How many locations? You can use the select() function and unique() to show the unique Districts of Berlin

```{r}
#YOUR CODE HERE
```

There are 12 Districts in Berlin.

```{r}
#YOUR CODE HER
```

There are 150 possible locations for crimes.

### Exercise 3 - Descriptive statistics

a) What is the district that had the least amount of bike thefts in 2019? Use the following tidyverse functions:

- filter(): for the year 2019
- select(): leave the important columns
- group_by(): we want to group by District
- summarise(): and get the sum of Bike thefts in each
- arrange(): to see which one had the least amout of thefts

```{r}
#YOUR CODE HERE
```

b) What were the total crimes of each category committed in your district in Berlin on 2019?

If you are not sure where your neighbourhood is, check out this map:
https://en.wikipedia.org/wiki/Boroughs_and_neighborhoods_of_Berlin#/media/File:Berlin,_administrative_divisions_(+districts_+boroughs_-pop)_-_de_-_colored.svg

Use filter() for the year and district, and select(-c()), to drop all columns that are not numeric

Use colSums() to get the total crimes of each category

```{r}
#YOUR CODE HERE
```

### Exercise 4 - Visualizing crimes

Fit the name of your district in the following code, we are going to use the package ggplot2() ♥

```{r}
district_2019 <- berlin_crimes %>% 
  filter(Year == 2019 & District == "write your district here") %>% 
  select(-c(Code, Location, Year, District)) 

data <- data.frame(colSums(district_2019))

data$crime_name <- row.names(data)
names(data) <- c("total", "crime_name")

barplot(sort(data$total), names= data$crime_name,
        horiz = TRUE, las = 1)
```


```{r}
ggplot(data, aes(x = total, y = reorder(crime_name, total))) +
  geom_col(fill = "cornflowerblue")+
  theme_minimal()
```

